The first high-redshift Changing Look Quasars

### 2019-12-02 tex/CIV_CLQs.tex
Massive general update

\documentclass[a4paper,fleqn,usenatbib]{mnras}

@@

\author[Ross {\it et al.}]
{%The RH John~S.~Bercow, MP, {\it et al.} 
Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
 Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,  Barry McKernan$^{3,4,5}$   
\newauthor Daniel Stern$^{6}$ and Giorgio Calderone$^{7}$
\\
% List of institutions
%$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
$^{3}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
$^{4}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
$^{5}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
$^{7}$INAF -- Osservatorio Astronomico di Trieste, Via Tiepolo 11, I-34143 Trieste, Italy \\
}

@@

\hypersetup{draft}

@@

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first ``Changing-Look'' quasars at
high redshift.  This is also the first time the changing-look
behaviour has been seen in a high-ionization emission line.  SDSS
J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour in
their observed optical light curves, and subsequent spectroscopy shows
significant changes in the \civ\ broad emission line, with both line
collapse and emergence being displayed in rest-frame timescales of
$\sim$240-1640 days.  Where observed, the profile of the
Ly$\alpha$/\nv emission complex also changes, and there is tentative
evidence for changes in the \mgii line.  Although line measurements
from the three quasars show large changes in the \civ\ flux-line width
plane, the quasars are not seen to be outliers when considered against
the full $z\sim2$ quasar population in terms of (rest) Equivalent
Width and FWHM properties.  We put these observations in context with
recent ``state-change'' models, but note that even in their
`low-state', the \civ\ CLQs are above $\sim$10\% in Eddington
luminosity.
\end{abstract}

@@

Using the multi-epoch spectra of 362 quasars from the Sloan Digital
Sky Survey Reverberation Mapping \citep[SDSS-RM; ][]{Shen2015,
Shen2019} project, \citet{Sun2018} investigate the blueshift of \civ\
emission relative to \mgii emission, and its dependence on quasar
properties.  These authors confirm that high-blueshift sources tend to
have low \civ\ EWs, and that the low-EW sources span a range of
blueshift. Other high-ionization lines, such as \heii, also show
similar blueshift properties. The ratio of the line width of \civ\ to
that of \mgii increases with blueshift.  \citet{Sun2018} also find
that quasar variability might slightly enhance the connection between
the \civ\ blueshift and EW, though further investigation here is
warranted.  There is also the finding that the objects with that
largest blueshifts are less variable and tend to have higher Eddington
ratios.  \citet{Sun2018} explain their results these by suggesting
that quasar SEDs become {\it softer} with {\it increasing Eddington
ratio} along with the presence of X-ray shielding by the inner
accretion disk.  However, a high Eddington ratio alone might be an
insufficient condition for the \civ\ blueshift.
%%
Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}. 
\citet{Dyer2019} provide a detailed analysis of 340 quasars at high-redshift
($1.62<z<3.30$) from the SDSS-RM project, which we will compare our
results to.

@@

This paper is organised as follows. In Section 2, we describe our
sample selection, catalogues, and observational data sets.  In Section
3, we show the high-$z$ quasars and report the line properties for the
quasars at the observed epochs.  We give a very brief theoretical
discussion in Section 4. We present our conclusions in Section 5.  We
report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
Fukugita1996} unless otherwise stated. For the WISE bands, $m_{\rm AB}
= m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1 at
3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively \citep{Cutri2011}. We
adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73 $,
$\Omega_{\rm M} = 0.27$, and $h = 0.71$. All logarithms are to the base 10.

@@

The ZTF is a new robotic time-domain sky survey capable of visiting
the entire visible sky north of -30 deg. declination every night. ZTF
observes the sky in the $g$, $r$, and $i$-bands at different cadences
depending on the scientific program and sky region
\citep{Bellm2019_ZTFSurveys, Graham2019_ZTF}. The ZTF 576 megapixel
camera with a 47 deg$^{2}$ field of view, installed on the Samuel
Oschin 48-inch Schmidt Telescope, can scan more than 3750 deg$^{2}$
per hour, to a 5$\sigma$ detection limit of 20.7 mag in the $r$-band
with a 30sec exposure during new moon \citep{Masci2019}.

@@

\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
  {figures/J1205+3422_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
  {figures/J1638+2827_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
  {figures/J2228+2201_landscape_20191112.png}
  \vspace{-12pt}
  \caption[]{The three high-$z$ CLQ quasars; 
    J1205+3422 (top), 
    J1638+2827 (middle) and  
    J2228+2201 (bottom). 
The light curve data is present in the panels on the left hand side, with the 
spectral epoch observational timings indicated by vertical lines. 
The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
complex, the \civ\ line, and the \mgii line. 
  }
  \label{fig:civ_clqs}
\end{figure*}
\subsection{Spectroscopy}
An overview of our spectroscopic observations is given in
Table~\ref{tab:obs_notes}.  The spectra are from the SDSS
\citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
Oscillation Spectroscopic Survey \citep[BOSS; ][]{Eisenstein2011,
Dawson2013, Smee2013, Alam2015, Paris2017} and the SDSS-IV Extended
Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
Abolfathi2018, Paris2018}.  These quasars were targetted via a range
of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
Myers2015}. The SDSS, BOSS, and eBOSS data are supplemented by
spectra from the Low Resolution Imaging Spectrometer \citep[LRIS; ][]{Oke1995} on the 10m
Keck {\sc I} telescope.  and the Double Spectrograph
(DBSP) instrument on the 200'' Palomar telescope.

@@

  \small
    \begin{tabular}{l  l | c c | c c c c | c}
              &          &  \multicolumn{2}{c}{Cont. @ 1450\AA }                  &   \multicolumn{4}{c}{CIV 1549\AA}                                                                                & Virial product \\
Object    & MJD  &      $\nu L_{\nu}$    &         Slope                             &   Luminosity         &     FWHM                 &    V$_{\rm off}$    & EW                                 & log($\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$) \\
 & & $10^{42}$ erg s$^{-1}$ & (F$_\lambda \propto \lambda^\alpha$)  & $10^{42}$ erg s$^{-1}$ &  km s$^{-1}$   &     km s$^{-1}$   &  \AA                              &  $\log(M/M_{\odot})$ \\
                     & 53498   &  38129  $\pm$ 39  &  -1.57 $\pm$ 0.01 &   898 $\pm$ 15    &   6024 $\pm$  120  &  944 $\pm$  33  & 37.78 $\pm$  0.62  &   9.85 $\pm$ 0.02\\
 J1205+3422 & 58538    &  8550 $\pm$ 11    &  -1.41 $\pm$ 0.01 &  385.2 $\pm$ 3.9 &   7109 $\pm$   91   & 1085 $\pm$  29  &   71.32 $\pm$  0.71  &   9.67 $\pm$ 0.01\\  
                     & 58693$^*$ & 2725 $\pm$ 40 &  -1.27 $\pm$ 0.05 &  161 $\pm$ 22    &  14997 $\pm$ 2500 &  922 $\pm$ 690  & 91.68 $\pm$ 12.73  &  10.07 $\pm$ 0.13\\  
                      &              &                               &                               &                              &                                 &                             &                                   &                              \\
                      & 54553   & 3579 $\pm$ 49    &  -1.16 $\pm$ 0.07  & 293.6  $\pm$ 8.8 &  4630 $\pm$  180   & 183 $\pm$  57   & 127.67 $\pm$  3.80  &    9.11 $\pm$ 0.04\\  
 J1638+2827 & 55832   & 2340 $\pm$ 15    &  -2.17 $\pm$ 0.05  &  84.6  $\pm$ 4.2  &  4733 $\pm$  290   & 172 $\pm$  89   &  59.61 $\pm$  2.98  &    9.04 $\pm$ 0.05\\  
                      & 58583  & 7793 $\pm$ 19     &  -2.02 $\pm$ 0.01  & 367.5  $\pm$ 4.3 &  4511 $\pm$   71    &  94 $\pm$  24   &  77.89 $\pm$  0.91  &  9.25 $\pm$ 0.01\\  
                      &             &                               &                                &                              &                                 &                            &                                   &                            \\
                     & 56189$^*$ & 607 $\pm$ 49  &  -0.00 $\pm$ 0.16 &  72.8  $\pm$ 11.3 & 14993 $\pm$ 2400 &  828 $\pm$ 691   & 162.89 $\pm$ 25.37  &  9.74 $\pm$ 0.14\\  
 J2228+2201 & 56960   & 7842 $\pm$ 25     &  -1.72 $\pm$ 0.02 & 301.0  $\pm$ 7.2  &  7136 $\pm$  210   & -276 $\pm$  64   &  61.99 $\pm$  1.48  &    9.65 $\pm$ 0.03\\ 
              & 58693   & 2388.4 $\pm$ 6.8 &  -1.22 $\pm$ 0.01 & 145.4  $\pm$ 1.5  &  6084 $\pm$   83    &   168 $\pm$  28   &  94.77 $\pm$  0.99  &    9.26 $\pm$ 0.01\\
    \caption{Continuum at 1450\AA\ and \civ\ spectral measurements for the
      three quasar considered in this work, at all observation epochs, as
      calculated by QSFit.  The last column shows the virial product
      calculated as $\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$.  $^{*}$The
      \civ\ line is very faint (with respect to the continuum), and the
      associated estimates are likely unreliable.}
    \label{tab:QSFit-results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Photometric and Overal Spectral Evolution}
Figure~\ref{fig:civ_clqs} presents the optical and mid-IR light
curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also
shows the spectra for each epoch, with the MJD of observation given by
the dashed vertical lines in the light curves.

For J1205+3422, our spectral observations cover 5195 days observed,
1691 days in the rest-frame. This quasar was initially identified in
SDSS in 2005 May, as a bright, $g\approx18.0$, blue-sloped quasar with
broad \siiv, \civ, \ciii and \mgii. \ciii and \civ\ have large
blueshifts of $\approx$2600$\pm$150 and $\approx$1150$\pm$100 km
s$^{-1}$, respectively.  By 2019, however, the opitical brightness
dropped by $\sim$1.5 magnitudes and the spectra are significantly less
blue.  While \lya and \nv are detectable in both 2019 spectra, \civ\
has all but disappeared in the 2019 June spectrum.  The broad \ciii
emission has disappeared between the 2005 and 2019 spectra. The
changes in \civ\ and \ciii going from broad emission to barely
detectable have on the timescales of $\approx$50 days in the
rest-frame.

@@

\subsection{\civ\ Emission Line Evolution}
We analyzed the spectra of the three quasars, at all observational
epochs, using the QSFit spectral fitting package
\citep{Calderone2017}.  One advantage of using QSFit is that it allows
constraints on the slope and luminosity of the broad band continuum of
the source. The relevant estimated quantities, including continuum
luminosity and slope at rest-frame 1450\AA, \civ\ line luminosity,
FWHM and EW are given in Tab.~\ref{tab:QSFit-results}. All fits are
performed with $E(B-V) = 0$ and the best fit model in the region of
the \civ\ emission line are shown in Figure~\ref{fig:QSFit-CIV}.

All \civ\ lines are fitted with a single, broad, Lorentzian profile.
This allows us to account for the narrow peak of the \civ\ line. 
No narrow components are considered for several reasons: in the epochs
of highest brightness the ``narrow'' component would have FWHM
$\sim2-3 \times 10^{3}$ km s$^{-1}$, i.e. values exceeding the usual
widths of genuine narrow lines ($\lesssim 10^3$ km s$^{-1}$); by
allowing a second component, to have such large widths their
parameters would become highly degenerate with the ``broad''
components, and the latter would also have much larger FWHM
($\sim10^{4}$ km s$^{-1}$); and by neglecting the narrow components we
have a consistent fit across all epochs.

The quasar continuum, evaluated at 1450\AA\ , and the \civ\ line
luminosities follow a similar evolution, with a ratio of $\sim$20-30,
confirming that the main driver for emission line variability is
likely the broad band continuum itself.  For all sources except
J1638+2827, the slope of the continuum changes with luminosity
following a ``bluer-when-brighter'' pattern, suggesting that a
distinct emerging component is responsible or both the slope and
luminosity variations.  In J1638+2827 the opposite behaviour is
observed, especially in the first observation epoch.  However, this
may be a bias due to the limited wavelength range available which
extends to $\lambda \sim 1240\AA$ for the first epoch, while it extend
to shorter wavelengths for the other epochs (respectively 1140\AA\ and
1010\AA).  The latter suggests that the ``emerging'' component is more
prominent at UV wavelengths, and a sufficient wavelength coverage is
required to detect it. We find there is no need for a narrow component
in J2228+2201 MJD 56189.  This is because the data resemble a P-Cygni
profile, with blueshifted absorption. This feature is very narrow, and
the uncertainties large, such that the overall $\chi^{2}$ is only
marginally affected by the addition of a further component. We
therefore avoid using a narrow component for this spectrum only, since
that would be inconsistent with the other analyses.

In all cases where the \civ\ line profile is reliably constrained the
\civ\ FWHM is approximately constant, with maximum variations
$\lesssim$~1000 km s$^{-1}$, despite the significantly larger
variations in the line luminosities.  The FWHM of broad lines is
likely related to the mass of the supermassive black hole powering the
quasar phenomenon, which is supposed to be constant on any human
timescale.  Hence it is instructive to check whether the virial
product, which is the basic quantity used to calculate the single
epoch mass estimate, show any variation.  The virial product,
calculated as $\nu L_{\nu}^{0.5} \times {\rm FWHM}^2$, is reported in
the last column of Tab.~\ref{tab:QSFit-results}.  The uncertainty
typically associated to the single epoch mass estimate is $\sim$0.5
dex, hence the virial product at all epochs are remarkably constant
and compatible with a single value of black hole mass for each source,
even in those cases where the \civ\ estimates are possibly
unreliable. The object showing larger variation is J2228+2201,
although the extreme values span a range of 0.48 dex.

Finally, also the velocity offsets of the \civ\ line are also
approximately constant, and compatible with a single value (within
3$\sigma$).  The exception is J2228+2201, where a significant change
($\sim$7$\sigma$) is observed between the second and third observation
epochs.

The temporal evolution of the velocity offsets, along with the
1450\AA\ continuum luminosity and slope, the \civ\ line FWHM
and virial black hole mass are given in Figure~\ref{fig:QSFit-results}.

%% trim={<left> <lower> <right> <upper>}
\begin{figure*}
  \centering
 \includegraphics[width=\textwidth, trim={0cm 0 0 0},clip]{figures/CIVregions.png}
%  \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-2089-53498-0427.png}
 % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J1205p3422_58538.png}
 % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J1205p3422_58693.png}\\
 % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-2948-54553-0614.png}
 % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-5201-55832-0178_v5_10_0.png}
 % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J1638p2827_58583.png}\\
 % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-6118-56189-0720.png}
 % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/spec-7582-56960-0790.png}
 % \includegraphics[width=.3\textwidth, trim={0cm 0 0 0},clip]{figures/J2228p2201_58693.png}
  \caption{Observed spectra and best fit model in the region relevant
    to \civ\ emission line for the quasars considered here.}
  \label{fig:QSFit-CIV}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figures/QSFit-results}
  \vspace{-12pt}
  \caption{Temporal evolution of the spectral properties of the three
    quasar considered in this work.}
  \label{fig:QSFit-results}
\end{figure*}

>>>>

\documentclass[fleqn,usenatbib]{mnras}

@@

\author[Ross {\it et al.}]
{Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
 Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,  Barry McKernan$^{3,4,5}$   
\newauthor Daniel Stern$^{6}$ and Giorgio Calderone$^{7}$
\\
%%  List of institutions
$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
$^{3}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
$^{4}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
$^{5}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
$^{7}$INAF -- Osservatorio Astronomico di Trieste, Via Tiepolo 11, I-34143 Trieste, Italy \\
}

@@

@@

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first ``Changing-Look'' quasars at
high redshift.  This is also the first time the changing-look
behaviour has been seen in a high-ionization emission line.  SDSS
J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour in
their observed optical light curves, and subsequent spectroscopy shows
significant changes in the \civ\ broad emission line, with both line
collapse and emergence being displayed in rest-frame timescales of
$\sim$240-1640 days.  These are very quick changes, especially when
considering virial black hole mass estimates have all three quasars
with $M_{\rm BH} > 10^{9} M_{\odot}$.  Continuum and emission line
measurements from the three quasars show changes in the
continuum-equivalent width plane with the CLQs seen to be on the edge
of the full population distribution, and showing indications of an
intrinsic Baldwin Effect. We put these observations in context with
recent ``state-change'' models, but note that even in their
`low-state', the \civ\ CLQs are above $\sim$10\% in Eddington
luminosity.
\end{abstract}

@@

Using the multi-epoch spectra of 362 quasars from the Sloan Digital
Sky Survey Reverberation Mapping \citep[SDSS-RM; ][]{Shen2015,
Shen2019} project, \citet{Sun2018} investigate the blueshift of \civ\
emission relative to \mgii emission, and its dependence on quasar
properties. These authors confirm that high-blueshift sources tend to
have low \civ\ EWs, and that the low-EW sources span a range of
blueshift. Other high-ionization lines, such as \heii, also show
similar blueshift properties. The ratio of the line width of \civ\ to
that of \mgii increases with blueshift. \citet{Sun2018} also find that
quasar variability might slightly enhance the connection between the
\civ\ blueshift and EW, though further investigation here is
warranted. There is also the finding that the objects with that
largest blueshifts are less variable and tend to have higher Eddington
ratios. \citet{Sun2018} explain their results these by suggesting that
quasar SEDs have weaker X-ray emission (or at least a larger UV/optical-to-Xray
spectral index, $\alpha_{\rm ox}$) and thus become {\it
softer} with {\it increasing Eddington ratio} along with the presence
of X-ray shielding by the inner accretion disk. However, a high
Eddington ratio alone might be an insufficient condition for the \civ\
blueshift. Recent investigations also include \citet{Meyer2019} and
\citet{Doan2019}. \citet{Dyer2019} provide a detailed analysis of 340
quasars at high-redshift ($1.62<z<3.30$) from the SDSS-RM project,
which we will compare our results to.

@@

This paper is organised as follows. In Section 2, we describe our
sample selection, catalogues, and observational data sets.  In Section
3, we show the high-$z$ quasars and report the line properties for the
quasars at the observed epochs.  We give a very brief theoretical
discussion in Section 4. We present our conclusions in Section 5.  We
report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
Fukugita1996} unless otherwise stated. For the WISE bands, $m_{\rm AB}
= m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1 at
3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively \citep{Cutri2011, Cutri2013}. We
adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73 $,
$\Omega_{\rm M} = 0.27$, and $h = 0.71$. All logarithms are to the base 10.

@@

The ZTF is a new robotic time-domain sky survey capable of visiting
the entire visible sky north of -30 deg. declination every night. ZTF
observes the sky in the $g$, $r$, and $i$-bands at different cadences
depending on the scientific program and sky region
\citep{Bellm2019_ZTFSurveys, Graham2019_ZTF}. The ZTF 576 megapixel
camera with a 47 deg$^{2}$ field of view, installed on the Samuel
Oschin 48-inch Schmidt Telescope, can scan more than 3750 deg$^{2}$
per hour, to a 5$\sigma$ detection limit of 20.7 mag in the $r$-band
with a 30sec exposure during new moon \citep{Masci2019}.
\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.45cm 0.1cm, clip]
  {figures/J1205+3422_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.05cm 0.40cm 0.1cm, clip]
  {figures/J1638+2827_landscape_20191112.png}
  \includegraphics[width=16.7cm, trim=0.3cm 0.0cm  0.35cm 0.1cm, clip]
  {figures/J2228+2201_landscape_20191112.png}
  \vspace{-12pt}
  \caption[]{The three high-$z$ CLQ quasars; 
    J1205+3422 (top), 
    J1638+2827 (middle) and  
    J2228+2201 (bottom). 
The light curve data is present in the panels on the left hand side, with the 
spectral epoch observational timings indicated by vertical lines. 
The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
complex, the \civ\ line, and the \mgii line. 
  }
  \label{fig:civ_clqs}
\end{figure*}

@@

%% From Section 3.1; Place here to help with overall formatting of
%% the paper
\input{QSFit-results}

\subsection{Spectroscopy}
An overview of our spectroscopic observations is given in
Table~\ref{tab:obs_notes}.  The spectra are from the SDSS
\citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
Oscillation Spectroscopic Survey \citep[BOSS; ][]{Eisenstein2011,
Dawson2013, Smee2013, Alam2015, Paris2017} and the SDSS-IV Extended
Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
Abolfathi2018, Paris2018}.  These quasars were targetted via a range
of techniques and algorithms \citep[see ][]{Richards2002, Ross2012,
Myers2015}. The SDSS, BOSS, and eBOSS data are supplemented by
spectra from the Low Resolution Imaging Spectrometer \citep[LRIS; ][]{Oke1995} on the 10m
Keck {\sc I} telescope.  and the Double Spectrograph
(DBSP) instrument on the 200'' Palomar telescope.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Photometric and Overal Spectral Evolution}
Figure~\ref{fig:civ_clqs} presents the optical and mid-IR light
curves for three high-$z$ CLQ quasars.  Figure~\ref{fig:civ_clqs} also
shows the spectra for each epoch, with the MJD of observation given by
the dashed vertical lines in the light curves.

For J1205+3422, our spectral observations cover 5195 days observed,
1691 days in the rest-frame. This quasar was initially identified in
SDSS in 2005 May, as a bright, $g\approx18.0$, blue-sloped quasar with
broad \siiv, \civ, \ciii and \mgii. \ciii and \civ\ have large
blueshifts of $\approx$2600$\pm$150 and $\approx$1150$\pm$100 km
s$^{-1}$, respectively.  By 2019, however, the optical brightness
dropped by $\sim$1.5 magnitudes and the spectra are significantly less
blue.  While \lya and \nv are detectable in both 2019 spectra, \civ\
has all but disappeared in the 2019 June spectrum.  The broad \ciii
emission has disappeared between the 2005 and 2019 spectra. The
changes in \civ\ and \ciii going from broad emission to barely
detectable have on the timescales of $\approx$50 days in the
rest-frame.

@@

%% trim={<left> <lower> <right> <upper>}
\begin{figure}
  \centering
  \includegraphics[width=8.40cm, trim=0.37cm 0.3cm 0.0cm 0.2cm, clip]{figures/CIVregions.png}
    \vspace{-18pt}
  \caption{Observed spectra and best fit model in the region relevant
    to \civ\ emission line for the quasars considered here.}
  \label{fig:QSFit-CIV}
\end{figure}
\subsection{\civ\ Emission Line Evolution}
We analyzed the spectra of the three quasars, at all observational
epochs, using the QSFit spectral fitting package
\citep{Calderone2017}.  One advantage of using QSFit is that it allows
constraints on the slope and luminosity of the broad band continuum of
the source. The relevant estimated quantities, including continuum
luminosity and slope at rest-frame 1450\AA, \civ\ line luminosity,
FWHM and EW are given in Tabl;e~\ref{tab:QSFit-results}. All fits are
performed with $E(B-V) = 0$ and the best fit model in the region of
the \civ\ emission line are shown in Figure~\ref{fig:QSFit-CIV}.

All \civ\ lines are fitted with a single, broad, Lorentzian profile.
This allows us to account for the narrow peak of the \civ\ line.  No
narrow components are considered for several reasons: in the epochs of
highest brightness the ``narrow'' component would have FWHM~$\sim2-3
\times 10^{3}$~km~s$^{-1}$, i.e. values exceeding the usual widths of
genuine narrow lines ($\lesssim$ $10^3$ km s$^{-1}$); by allowing a
second component, to have such large widths their parameters would
become highly degenerate with the ``broad'' components, and the latter
would also have much larger FWHM ($\sim$$10^{4}$ km s$^{-1}$); and by
neglecting the narrow components we have a consistent fit across all
epochs.

The quasar continuum, evaluated at 1450\AA\ , and the \civ\ line
luminosities follow a similar evolution, with a ratio of $\sim$20-30,
confirming that the main driver for emission line variability is
likely the broad band continuum itself.  For all sources except
J1638+2827, the slope of the continuum changes with luminosity
following a ``bluer-when-brighter'' pattern, suggesting that a
distinct emerging component is responsible or both the slope and
luminosity variations.  In J1638+2827 the opposite behaviour is
observed, especially in the first observation epoch.  However, this
may be a bias due to the limited wavelength range available which
extends to $\lambda \sim 1240$\AA\ for the first epoch, while it extend
to shorter wavelengths for the other epochs (respectively 1140\AA\ and
1010\AA).  The latter suggests that the ``emerging'' component is more
prominent at UV wavelengths, and a sufficient wavelength coverage is
required to detect it. We find there is no need for a narrow component
in J2228+2201 MJD 56189.  This is because the data resemble a P-Cygni
profile, with blueshifted absorption. This feature is very narrow, and
the uncertainties large, such that the overall $\chi^{2}$ is only
marginally affected by the addition of a further component. We
therefore avoid using a narrow component for this spectrum only, since
that would be inconsistent with the other analyses.
In all cases where the \civ\ line profile is reliably constrained the
\civ\ FWHM is approximately constant, with maximum variations
$\lesssim$~1000 km s$^{-1}$, despite the significantly larger
variations in the line luminosities.

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_MBHvsREW_QSFit20K.png}
   \vspace{-12pt}
   \caption[]{The virial black hole masses of $\approx$20,000 $z>1.5$ quasars
     from QSFit catalogue \citep{Calderone2017} and the \civ\ Equivalent widths.
     Different quasars are given different colours: J1205+3422 purple; J1638+2827 green; J2228+2201 is blue.
     Different epochs different symbols: first epoch circles; second epoch squares; third epoch diamonds. 
   }
  \label{fig:CIV_MBHvsREW}
\end{figure}
\subsection{Virial Black Hole Masses}
The FWHM of broad lines is likely related to the mass of the
supermassive black hole powering the quasar phenomenon, which is
assumed to be constant on any human timescale.  Hence it is
instructive to check whether the virial product, which is the basic
quantity used to calculate the single epoch black hole mass estimate,
show any variation.

Using the estimates for the continuum luminosity and FWHW from the
single-epoch spectra, one can estimate the central black hole mass
\citep[e.g.][]{Shen2011, Calderone2017}.  This approach assumes that
the broad-line region (BLR) is virialized, the continuum luminosity is
used as a proxy for the BLR radius, and the broad line width (FWHM) is
used as a proxy for the virial velocity.  This ``virial mass''
estimate can then be expressed as:
\begin{equation}
  \log(M_{\rm BH}) = (\nu L_{\nu})^{\gamma} \times ({\rm FWHM})^{\delta}
\end{equation}
where $\gamma=0.5$ and $\delta=2$.  The virial product for the \civ\
CLQs is reported in the last column of Tab.~\ref{tab:QSFit-results}. 
The uncertainty typically associated to the single epoch mass estimate
is $\sim$0.5 dex, hence the virial product at all epochs are
remarkably constant and compatible with a single value of black hole
mass for each source, even in those cases where the \civ\ estimates
are possibly unreliable. The object showing larger variation is
J2228+2201, although the extreme values span a range of 0.48 dex.

From the virial mass estimates, all our objects have SMBH masses $M >10^{9} M_{\odot}$.
This is at the upper end of SMBH masses at all epochs, and towards the
extreme of the mass distribution for $z\sim2$ objects.  
Figure~\ref{fig:CIV_MBHvsREW} shows the \civ\ Equivalent width and the
virial black hole masses for a sample of $\approx$20,000 $z>1.5$ SDSS
quasars from the QSFit catalog as well as the estimates for the three
\civ\ CLQs.

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191128.png}
  \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
    of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
    of \citet{Hamann2017}.
   Symbols as in Fig.~\ref{fig:CIV_MBHvsREW}.}
  \label{fig:REWvsFWHM}
\end{figure}
\subsection{Quantified Temporal Evolution of \civ\ Emission}
Figure~\ref{fig:REWvsFWHM} shows the rest Equivalent Width (REW)
versus the Full Width Half Maximum (FWHM) of the \civ\ emission line
in the BOSS DR12 quasar sample using the catalogue of
\citet{Hamann2017}.

The velocity offsets of the \civ\ line are also
approximately constant, and compatible with a single value (within
3$\sigma$).  The exception is J2228+2201, where a significant change
($\sim$7$\sigma$) is observed between the second and third observation
epochs.
